% backmatter/05_tai_lieu_tham_khao.tex
\addcontentsline{toc}{chapter}{TÀI LIỆU THAM KHẢO}
\begin{thebibliography}{99}

\bibitem{rfc3031}
E. Rosen, A. Viswanathan, R. Callon,
\textit{Multiprotocol Label Switching Architecture},
RFC 3031, IETF, January 2001.
Available: \url{https://www.rfc-editor.org/rfc/rfc3031}

\bibitem{rfc3985}
S. Bryant, P. Pate (Eds.),
\textit{Pseudo Wire Emulation Edge-to-Edge (PWE3) Architecture},
RFC 3985, IETF, March 2005.
Available: \url{https://www.rfc-editor.org/rfc/rfc3985}

\bibitem{rfc5036}
L. Andersson, I. Minei, B. Thomas (Eds.),
\textit{LDP Specification},
RFC 5036, IETF, October 2007.
Available: \url{https://www.rfc-editor.org/rfc/rfc5036}

\bibitem{rfc2328}
J. Moy,
\textit{OSPF Version 2},
RFC 2328, IETF, April 1998.
Available: \url{https://www.rfc-editor.org/rfc/rfc2328}

\bibitem{rfc4271}
Y. Rekhter, T. Li, S. Hares (Eds.),
\textit{A Border Gateway Protocol 4 (BGP-4)},
RFC 4271, IETF, January 2006.
Available: \url{https://www.rfc-editor.org/rfc/rfc4271}

\bibitem{mef6}
Metro Ethernet Forum,
\textit{Ethernet Services Definitions -- Phase I},
MEF 6, November 2004.
Available: \url{https://www.mef.net/}

\bibitem{mef10}
Metro Ethernet Forum,
\textit{Ethernet Services Attributes Phase I},
MEF 10, October 2004.

\bibitem{mininet}
B. Lantz, B. Heller, N. McKeown,
\textit{A Network in a Laptop: Rapid Prototyping for Software-Defined Networks},
In: Proceedings of the 9th ACM SIGCOMM Workshop on Hot Topics in Networks (HotNets-IX), 2010.
Available: \url{http://mininet.org/}

\bibitem{ovs}
B. Pfaff et al.,
\textit{The Design and Implementation of Open vSwitch},
In: 12th USENIX Symposium on Networked Systems Design and Implementation (NSDI'15), 2015.

\bibitem{frr}
FRRouting Project,
\textit{FRRouting User Guide}, Version 9.x, 2024.
Available: \url{https://docs.frrouting.org/}

\bibitem{cisco3tier}
Cisco Systems,
\textit{Campus Network for High Availability Design Guide},
Cisco Validated Design, 2013.
Available: \url{https://www.cisco.com/c/en/us/td/docs/solutions/Enterprise/Campus/HA_campus_DG/}

\bibitem{leafspine}
Arista Networks,
\textit{Leaf-Spine Architecture in Modern Data Centers},
White Paper, 2020.
Available: \url{https://www.arista.com/}

\bibitem{iproute2}
S. Almesberger,
\textit{Linux Advanced Routing \& Traffic Control HOWTO},
2012.
Available: \url{https://lartc.org/}

\bibitem{kernelmpls}
R. Schauer,
\textit{MPLS for Linux kernel},
Linux Kernel Documentation, 2017.
Available: \url{https://www.kernel.org/doc/Documentation/networking/mpls-sysctl.txt}

\bibitem{iperf3}
ESnet / Lawrence Berkeley National Laboratory,
\textit{iPerf3 -- The network bandwidth measurement tool},
2024.
Available: \url{https://iperf.fr/}

\end{thebibliography}